The population of long-period exoplanets --- \\ Fully-automated discovery \& characterization of long-period transiting exoplanet candidates in the \kepler\ archive \vspace{-3\baselineskip}

### 2016-06-29 document/ms.tex
masking transits

We also restrict the sample to only include targets with a data span of more
than two years and a duty cycle of better than $0.6$.
Since the \kepler\ data have been searched for shorter period planets
\dfmtodo{CITE Coughlin} and eclipsing binaries \dfmtodo{CITE EB catalog} than
targeted by this project, we censor these previously known targets.
For the known EBs, we simply remove these targets from the candidate list.
For the confirmed and candidate KOIs from \dfmtodo{Coughlin}, we remove data
within 2 transit durations of the known candidates.

>>>>

Since these data have already been searched for short-period planets, we
assume that all high signal-to-noise candidates with three or more transits
have been previously found \citep{Coughlin:2016}.
To remove these candidates from consideration, we mask the cadences within two
transit durations of the time when a short-period planet candidate is known to
transit.
